Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-30 Draft/Draft.Rmd
meso-scale analyses update

We follow Simmons et al. to decompose networks on their constituent motifs. We compare observed motif frecuancies to vaznull model, which constrains the number of plants, pollinators and the network connectance. For each network we compared the observed motif frequency with the expected frecuancies and ... . To summarize general patterns across networks we used a GLMM per motif with the percentile per network, ...

Next, we calculated which functional groups were over or under-represented in different motif positions by comparing with ... . Again, we tested ...

>>>>

Following Simmons et al. [@simmons2019,@simmons2020], we broke down the plant-pollinator networks into their constituent motifs. Prior to analyses, we selected only robust links, that is, interactions whose frequency was greater than one (64.94 % interactions); and, then, we turned the quantitative networks into qualitative (or binary) ones, where interactions are present or absent.

We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical and simulated network, by using the ‘bmotif’ package [@bmotifsimmons2019]. To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we excluded from our analyses two-node motifs (or links) because their normalised frequency would always equal one.

To assess the significance of the observed frequencies, we created 1,000 simulated networks for each binary network using the ‘nullmodel’ function and the ‘vaznull’ model in the bipartite package [@dormann2009]. Generated networks had the same number of plants and pollinators, and the same connectance of their corresponding empirical networks. After extracting the motif frequencies from the simulated networks, we calculated the percentage of simulated networks whose motif frequencies were smaller than the observed frequency for each motif type and empirical network, that is, we estimated the percentile of the observed motif frequencies. Motifs whose percentile is close to zero or 100 are under- or over-represented in the empirical networks, respectively, and, thus, they cannot be predicted by connectance and the number of species alone. To summarize general patterns across networks, we used an intercept-only linear mixed model (LMM) per motif, where the response variable was the observed motif percentile per network. In these models, we used the study identifiers in Table S1 as a random intercept. By doing so, we obtained estimates of the average motif frequency, in which we controlled the variation at the study level.

Next, we calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated networks. For each network, we extracted the position frequencies of all motifs from three to five nodes for each species by using the ‘bmotif’ package [@bmotifsimmons2019]. To estimate the position frequencies of each functional in a given network, we added the frequencies of those species that belong to the same group and we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class. Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did motif frequencies. To  outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network. We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept. By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level. To fit the LMMs models in our analyses, we used the ‘lmer’ package [@bates2015].
